### 2016-09-23 paper/abstract.tex
added variable information on master file to each file
revised sections 1-5
Some thoughts on the paper

The growing dependence on big data makes reliably converting
between different data formats increasingly important.
\emph{Lenses} are a bi-directional technique for specifying such
conversions.  Specifically, a lens is a declarative program that
simultaneously specifies a function to convert data from type $A$ to
type $B$ and a second function to convert data from type $B$ to type
$A$.  Such programs usually provide invertibility guarantees, avoiding
pernicious bugs that can corrupt data and downstream processing.
Unfortunately, lenses can be quite difficult to write because they
require programmers to think in two directions at once.  To overcome
this difficulty, we develop an algorithm to automatically synthesize
lenses from format descriptions, specified as regular expressions, and
a small number of examples.  The rich structure of regular expressions
makes lens synthesis more complicated than previous work on other
forms of type-directed synthesis.  Specifically, finding a term to
bi-directionally map between regular expressions $A$ and $B$ requires
first finding equivalent regular expressions $A'$ and $B'$ that are
more algorithmically tractable.
We show how to manage this search by defining a new language of
lenses governed by semi-canonical regular expression types and prove it
sound with respect to a standard language of bijective lenses.  
We then show
how to search the reduced space for well-typed lenses that are consistent
with the given examples.  We demonstrate the effectiveness of our algorithm
by experimenting on a benchmark suite containing 42 examples
comprising microbenchmarks, Flash Fill
examples, and Augeas transformations of Linux configuration files.
We show we are able to infer lenses for most examples in the
benchmark suite in an average of 0.134 seconds.

>>>>

The growing dependence on big data makes reliably converting
between different data formats increasingly important\bcp{This seems both
  contentious and not terribly relevant}.
\emph{Lenses} are a bi-directional technique for specifying such
conversions.  Specifically, a lens is a declarative program that
simultaneously specifies a function to convert data from type $A$ to
type $B$ and a second function to convert data from type $B$ to type
$A$.  Such programs usually provide invertibility guarantees, avoiding
pernicious bugs that can corrupt data and downstream processing.
Unfortunately, lenses can be quite difficult to write because they
require programmers to think in two directions at once.  To overcome
this difficulty, we develop an algorithm to automatically synthesize
lenses\bcp{just bijective ones!} from format descriptions, specified as regular expressions, and
a small number of examples.  The rich structure of regular expressions
makes lens synthesis more complicated than previous work on other
forms of type-directed synthesis.  Specifically, finding a term to
bi-directionally map between regular expressions $A$ and $B$ requires
first finding equivalent regular expressions $A'$ and $B'$ that are
more algorithmically tractable.
We show how to manage this search by defining a new language of
lenses governed by semi-canonical regular expression types and prove it
sound with respect to a standard language of bijective lenses.  
We then show
how to search the reduced space for well-typed lenses that are consistent
with the given examples.  We demonstrate the effectiveness of our algorithm
by experimenting on a benchmark suite containing 42 examples
comprising microbenchmarks, Flash Fill
examples, and Augeas transformations of Linux configuration files.
We show we are able to infer lenses for most\bcp{!} examples in the
benchmark suite in an average of 0.134 seconds \afm{TODO: automatically calculate this from CSV}.

### 2016-09-23 paper/introduction.tex
Some thoughts on the paper

@@

Bidirectional programming is used heavily in practice.
Augeas~\cite{?}, a configuration editing system for linux, uses lens combinators
to provide editable views of configuration files.
Bixid~\cite{?} is a language developed for expressing bidirectional XML
transformations.
XSugar~\cite{?} is used to convert bidirectionally between XML and non-XML data,
and is used to convert between EpiDoc~\cite{?} and Leiden+~\cite{?} formats for
encoding ancient documents~\cite{?}.
Serializers and deserializers combine to make a bidirectional program, though
they are rarely written in a domain specific language for bidirectional
programming.

>>>>

\bcp{May I make another plea for putting the whole paper into one big .tex
  file?}

@@

Bidirectional programming is used heavily in practice.\bcp{This may be
  overstating the case, for lenses per se.  Augeas is the only real-world
  example AFAIK.}
Augeas~\cite{?}, a configuration editing system for linux, uses lens combinators
to provide editable views of configuration files.
Bixid~\cite{?} is a language developed for expressing bidirectional XML
transformations.
XSugar~\cite{?} is used to convert bidirectionally between XML and non-XML data,
and is used to convert between EpiDoc~\cite{?} and Leiden+~\cite{?} formats for
encoding ancient documents~\cite{?}.
Serializers and deserializers combine to make a bidirectional program, though
they are rarely written in a domain specific language for bidirectional
programming.
